---
output: github_document
always_allow_html: yes
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# qsurvey

[![Build Status](https://travis-ci.org/jamesdunham/qsurvey.svg?branch=master)](https://travis-ci.org/jamesdunham/qsurvey)
[![CRAN Status Badge](http://www.r-pkg.org/badges/version/qsurvey)](https://cran.r-project.org/package=qsurvey)

qsurvey is a toolkit for working with the Qualtrics survey platform and its data
in R. It focuses on testing and review of surveys before fielding, and analysis
of responses afterward. 


## Installation

Install the latest version from GitHub:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("jamesdunham/qsurvey")
```

## Usage

```{r}
library(qsurvey)
```

A [Qualtrics API
key](https://www.qualtrics.com/support/integrations/api-integration/api-integration)
is needed to communicate with the survey platform. Set the environment variable
`QUALTRICS_KEY` to your key value. You can do this [during R
startup](https://www.rdocumentation.org/packages/base/versions/3.3.1/topics/Startup)
(recommended), interactively with
[`Sys.setenv()`](https://www.rdocumentation.org/packages/base/versions/3.3.1/topics/Sys.setenv),
or through `key_from_file()`.

Qualtrics assigns each survey a unique id. You can search by survey name for an
id using `find_id()`. Use `surveys()` to see the ids and other metadata for all
surveys, in a table similar to the Qualtrics Control Panel overview.


### Survey responses

Pass a survey's id to `responses()` to retrieve responses. This is equivalent to
using the "Export Data" tool in the "Data and Analysis" view of the Control
Panel and then reading the resulting file into R.   

```{r}
r <- responses(id = "SV_0CGgkDZJaUvxnGl", verbose = FALSE)
```

For functions that work with survey responses see `names_to_ids()` and
`drop_meta()`.


### Survey design

To retrieve a survey's design use `design()`. This returns a `qualtrics_design`
object that many other qsurvey functions can operate on. 

```{r}
d <- design(id = "SV_0CGgkDZJaUvxnGl")

print(d)
```

For example, use `questions()` to see the text and other attributes of each
survey question.

```{r}
svy_q <- questions(design_object = d)

svy_q[1:2, ]  
```

See also `choices()`, `blocks()`, and `response_counts()`.


### Visualization

Visualize a survey flow with `plot_flow()`. Or for interactive review of a
survey's flow and content in a Shiny app, use `render_flow()`.

```{r}
plot_flow(design_object = d)
```

See also `edges()` and `nodes()`.


## Related

* [qualtRics](https://github.com/JasperHG90/qualtRics) is another R package for
working with the Qualtrics API that began around the same time as qsurvey.

* [qualtricsR](https://github.com/saberry/qualtricsR) focuses on survey creation.

* I'm aware of two R packages for earlier versions of the Qualtrics API. [Jason
  Bryer](https://github.com/jbryer/qualtrics) wrote one in 2012. [Eric
  Green](https://github.com/ericpgreen/qualtrics) forked and revised it for v2.3
  of the Qualtrics API, most recently in 2014. 

* [QualtricsTools](https://github.com/ctesta01/QualtricsTools) generates reports
  from Qualtrics data via Shiny.

* Python: [PyQualtrics](https://github.com/Baguage/pyqualtrics);
  [SurveyHelper](https://github.com/cwade/surveyhelper).
