---
title: Responses
output: github_document
always_allow_html: yes
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

This vignette shows how to use qsurvey to download and work with responses
collected with the Qualtrics survey platform. Before continuing you should have
installed qsurvey; see the [installation instructions](https://jdunham.io/qsurvey/).

```{r}
library(qsurvey)
```

## Retrieve survey responses

We'll start by downloading the responses to a survey called "Demographics."

```{r}
(survey_id <- find_id("Demographics"))
```

`responses()` sends a request to the Qualtrics API for our response data and
waits while the survey platform prepares the export. After downloading it,
`responses()` returns the data.

```{r}
demographics = responses(survey_id)
class(demographics)
dim(demographics)
```

By default, `responses()` gives a table showing choice text or labels. This
means that if the respondent-facing answer choices for a question are `"Low"`,
`"Medium"`, and `"High"`, the response data will contain these strings.
Alternatively, if argument `use_labels = FALSE`, the response data will show
the choice ids `"1"`, `"2"`, and `"3"`, or if choice recodes have been
configured, perhaps `"-1"`, `"0"`, and `"1"`.

```{r}
head(demographics$Q23)
demographics_nolabels = responses(survey_id, use_labels = FALSE)
head(demographics_nolabels$Q23)
```

As described in the documentation for `response()`, other [Qualtrics API
parameters](https://api.qualtrics.com/docs/json) that affect the format of
survey responses are available. For example, passing argument
seenUnansweredRecode = "99" to `responses()` will show `"99"` as the response to
unanswered questions instead of `NA`, the default. See the [Qualtrics
documentation](https://api.qualtrics.com/docs/json) if you need to customize
output from `responses()`.


## Dropping columns

Let's take a look at the columns in the response data. The first five are survey
and respondent metadata. If they aren't useful to us, we can drop them with the
`drop_meta()` function. We're left with actual survey responses and the eight
columns named `DO-*` that give question display orders. 

```{r}
names(demographics)
demographics <- drop_meta(demographics)
names(demographics)
```

`drop_sensitive()` and `keep_questions()` are similar to `drop_meta()`, but
target different column ranges.


## Renaming variables

By default, the response table's variable names are the descriptive export names
given to each question in the Qualtrics Control Panel. Let's instead name them
according to the unique identifiers of questions. We'll need the survey's design
to access these; we pass it and the table of responses to `names_to_ids()`.

```{r}
demo_design <- design(survey_id)
demographics <- names_to_ids(demographics, demo_design)
names(demographics)
```

`ids_to_names()` does the reverse.

```{r}
# FIXME: need to preserve suffixes for eg Q5_1, Q5_2   
# demographics <- ids_to_names(demographics, demo_design)
# names(demographics)
```


## Conclusion

After downloading survey response data with `responses()`, two sets of
convenience functions are available: one for dropping/keeping columns, and
another for renaming columns. If you have a question or suggestion, please open
a [GitHub issue](https://github.com/jamesdunham/qsurvey/issues).
